### 2012-12-19 htdocs/anchoring.tex
Added to htdocs on surface anchoring
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig/trunk@1844 40876441-3496-0410-a613-a2fca35b2ae2

There is also a surface term (an area density)
\begin{equation}
f_s = {\textstyle\frac{1}{2}} w (Q_{\alpha\beta} - Q_{\alpha\beta}^0)^2
\end{equation}
where $Q^0_{\alpha\beta}$ is the preferred order parameter configuration
at the surface (to be either normal or planar).

The boundary condition we wish to apply are the Euler-Lagrange equations. 
They are at the surface of the particle
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}} = 0
\end{equation}
where $Q_{\alpha\beta,\gamma} = \partial_\gamma Q_{\alpha\beta}$. Here,
$n_\gamma$ is the outward unit normal at the surface (pointing into the
fluid) \cite{skarabot}. Note that compared to the regular minimization as  
explained in \cite{wright} this is a surface integral term that would 
usually vanish in the bulk.
With the
addition of the surface term we obtain
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}}
+ \frac{\partial f_s}{\partial Q_{\alpha\beta}} = 0.
\end{equation}
The derivative of the distortion free energy with respect to
$Q_{\alpha\beta,\gamma}$ gives
\begin{equation}
\kappa_0 n_\beta \partial_\gamma Q_{\alpha\gamma}
+ \kappa_1 n_\gamma
(\partial_\gamma Q_{\alpha\beta} - \partial_\alpha Q_{\gamma\beta})
- 2\kappa_1 q_0 n_\gamma \epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}.
\end{equation}
However, if we want a symmetric form (the derivative with respect to
$Q_{\beta\alpha,\gamma}$ is just as good) we can write this as
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha}).
\end{eqnarray}
If we add the derivative of the surface free energy,
where we assume that the preferred orientation $Q_{\alpha\beta}^0$ is
independent of $Q_{\alpha\beta}$, we get a full boundary condition
for the gradient of the tensor order parameter at the solid-fluid boundary:
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w(Q_{\alpha\beta} - Q_{\alpha\beta}^0) = 0.
\label{cholesteric_bc}
\end{eqnarray}

>>>>

There is also a surface term (an area density)
\begin{equation}
f_s = {\textstyle\frac{1}{2}} w_1 (Q_{\alpha\beta} - Q_{\alpha\beta}^0)^2
\end{equation}
where $Q^0_{\alpha\beta}$ is the preferred order parameter configuration
at the surface (in the case of normal anchoring or fixed planar anchoring).
For degenerate planar anchoring,
following Fournier and Galatola \cite{fournier2005}, we have
\begin{equation}
f_s = {\textstyle\frac{1}{2}} w_1 (\tilde{Q}_{\alpha\beta}
    - \tilde{Q}^\perp_{\alpha\beta})^2
    + {\textstyle\frac{1}{2}} w_2 (\tilde{Q}_{\alpha\beta}
                      \tilde{Q}_{\alpha\beta} - S^2_0)^2
\end{equation}
where $\tilde{Q}_{\alpha\beta} + (1/3)S_0 \delta_{\alpha\beta}$, $S_0$ is
is a fixed surface amplitude; to obtain a prefered degenerate
configuration we take the fluid order parameter $Q_{\alpha\beta}$ and
project $\tilde{Q}^\perp_{\alpha\beta} = P_{\alpha\gamma}
\tilde{Q}_{\gamma\sigma}
P_{\sigma\beta}$, where $P_{\alpha\beta} = \delta_{\alpha\beta}
- n_\alpha n_\beta$ and $n_\alpha$ is the local unit surface normal.

The boundary condition we wish to apply are the Euler-Lagrange equations. 
They are at the surface of the particle
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}} = 0
\end{equation}
where $Q_{\alpha\beta,\gamma} = \partial_\gamma Q_{\alpha\beta}$. Here,
$n_\gamma$ is the outward unit normal at the surface (pointing into the
fluid) \cite{skarabot}. Note that compared to the regular minimization as  
explained in \cite{wright} this is a surface integral term that would 
usually vanish in the bulk.
With the
addition of the surface term we obtain
\begin{equation}
n_\gamma \frac{\partial f}{\partial Q_{\alpha\beta,\gamma}}
+ \frac{\partial f_s}{\partial Q_{\alpha\beta}} = 0.
\end{equation}
The derivative of the distortion free energy with respect to
$Q_{\alpha\beta,\gamma}$ gives
\begin{equation}
\kappa_0 n_\beta \partial_\gamma Q_{\alpha\gamma}
+ \kappa_1 n_\gamma
(\partial_\gamma Q_{\alpha\beta} - \partial_\alpha Q_{\gamma\beta})
- 2\kappa_1 q_0 n_\gamma \epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}.
\end{equation}
However, if we want a symmetric form (the derivative with respect to
$Q_{\beta\alpha,\gamma}$ is just as good) we can write this as
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha}).
\end{eqnarray}
If we add the derivative of the surface free energy,
where we assume that the preferred orientation $Q_{\alpha\beta}^0$ is
independent of $Q_{\alpha\beta}$, we get a full boundary condition
for the gradient of the tensor order parameter at the solid-fluid boundary:
\begin{eqnarray}
{\textstyle\frac{1}{2}} \kappa_0 (n_\alpha \partial_\gamma Q_{\beta\gamma}
+ n_\beta \partial_\gamma Q_{\alpha\gamma})
+ \kappa_1 n_\gamma \partial_\gamma Q_{\alpha\beta}
- {\textstyle\frac{1}{2}} \kappa_1 n_\gamma ( \partial_\alpha Q_{\gamma\beta}
+ \partial_\beta Q_{\gamma\alpha})
\nonumber
\\
- \kappa_1 q_0 n_\gamma (\epsilon_{\alpha\gamma\sigma} Q_{\sigma\beta}
+ \epsilon_{\beta\gamma\sigma}Q_{\sigma\alpha})
- w_1(Q_{\alpha\beta} - Q_{\alpha\beta}^0) = 0.
\label{cholesteric_bc}
\end{eqnarray}
Note that for planar generate anchoring, the final term (the `surface
molecular field') is replaced by
\begin{equation}
- w_1 (\tilde{Q}_{\alpha\beta} - \tilde{Q}^\perp_{\alpha\beta})
- 2w_2 (\tilde{Q}_{\gamma\sigma} \tilde{Q}_{\gamma\sigma} - S^2_0)
  \tilde{Q}_{\alpha\beta}. 
\end{equation}
